Results

### 2019-02-27 02_analysis.Rmd
Include point estimates in tables

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Median difference in donation likelihood", y = NULL, tag = "D") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = theta_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
```

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Median difference in amount donated", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Median difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Median difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `∆` = mu_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-1.md"))
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `∆` = mu_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-2.md"))
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, `∆` = mu_diff, `%∆` = pct_change,
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-3.md"))
```

>>>>

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation across single conditions; values represent posterior medians {#tbl:likely-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-1.md"))
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-2.md"))
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `∆` = theta_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between likelihood of donation in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:likely-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-likely-diffs-3.md"))
```

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval; thin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos() +
  theme(panel.grid.major.y = element_blank())

@@

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
  group_by(title) %>% 
  mutate(group_id = 1:n()) %>% 
  mutate(term = case_when(
    term == "mu" ~ paste0(term, "_", group_id),
    TRUE ~ term
  )) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  ungroup()

@@

tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown −\nNo crackdown",
                        Issue = "Humanitarian\nassistance −\nHuman rights",
                        Funding = "Private −\nGovernment\nfunding")) %>% 
  mutate(title = fct_inorder(title)) %>% 
  select(`Frame` = title, `Amount~treatment~` = mu_2, `Amount~control~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated across single conditions; values represent posterior medians {#tbl:amount-diffs-1}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-1.md"))
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  select(Frame = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-2}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-2.md"))
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE, results="asis"}
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  select(`Issue frame` = Issue, `Funding frame` = Funding, 
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `∆` = mu_diff, `%∆` = pct_change, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(caption = 'Difference between amount donated in "crackdown" (treatment) and "no crackdown" (control) conditions; values represent posterior medians {#tbl:amount-diffs-3}') %T>%
  cat() %>% 
  cat(file = here("output", "tables", "tbl-amount-diffs-3.md"))
```
